---
title: "Aes Attribute in R"
author: Monalisa Roy
output: html_notebook
---

### Read the data

```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)
```
### Install packages

```{r}
install.packages("ggplot2")
library(ggplot2)
```



### Create the following bar-plot where
## PhoneService column is assigned to the x aesthetic
```{r}
ggplot(data = customer,aes(x=PhoneService))+geom_bar(fill="lightblue",col="black")
```


## Gender column is assigned to the x aesthetic
```{r}
ggplot(data = customer,aes(x=gender))+geom_bar(fill="coral",col="black")
```


## InternetService is assigned to x aesthetic and MonthlyCharges to aesthetic
```{r}
ggplot(data = customer,aes(x=InternetService,fill=MonthlyCharges))+geom_bar(col="red")

```


## MonthlyCharges is assigned to x aesthetic and SeniorCitizen to aesthetic
```{r}
ggplot(data = customer,aes(x=MonthlyCharges,fill=SeniorCitizen))+geom_bar(col="coral")

```


## TotalCharges is assigned to x aesthetic and tenure to aesthetic
```{r}
ggplot(data = customer,aes(x=TotalCharges,fill=tenure))+geom_bar(col="purple")

```


## StreamingTV is assigned to x aesthetic and SeniorCitizen to aesthetic
```{r}
ggplot(data = customer,aes(x=StreamingTV,fill=SeniorCitizen))+geom_bar(col="cyan3")

```


## Dependents is assigned to x aesthetic and Partner to aesthetic
```{r}
ggplot(data = customer,aes(x=Dependents,fill=Partner))+geom_bar(col="deeppink")

```








