---
title: "Array"
author: "Monalisa Roy"
output: html_notebook
---


### Read the data,load libraries
```{r}

customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)

placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
View(placement)

```


### Create an array as per the given data:

## An array named array_total_charges that contains the first 10 values from the total charges column.
```{r}
array(data=customer$TotalCharges[1:10],dim = 10)->array_total_charges
array_total_charges
```



## An array named array_monthly_charges that contains the first 5 values from the monthly charges column.
```{r}

array(data=customer$MonthlyCharges[1:5],dim = 5)->array_monthly_charges
array_monthly_charges
```


### Create an array using placement dataset that comprises of:

## Data of first 15 values from salary column.
```{r}
array(data = placement$salary[1:15],dim=15)->array_salary
array_salary
```



## Data of first 5 values from mba_p column.
```{r}
array(data = placement$mba_p[1:5],dim = 5)->array_mba_p
array_mba_p
```



## Data of first 10 values from e_test column.
```{r}
array(data = placement$etest_p[1:10],dim = 10)->array_etest_p
array_etest_p
```



