---
title: "Data visualization"
author: Monalisa Roy
output: html_notebook
---

### Read the data


```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
```

### Loading the relevant plotting library

* We are going to use ggplot here. If it is not installed, then un-comment the line install(ggplot2) 

```{r}
#install(ggplot2)
library(ggplot2)
```

### Creating plots

* We create a bar-plot for a column, say 'PaymentMethod'.

```{r}
plot(customer$PaymentMethod)
```
### Coloring

* Assigning the color 'burlywood4'.


```{r}
plot(customer$PaymentMethod,col="burlywood4")
```
### Naming the axes

* We assign the x-axis label to the 'Payment Method'.

```{r}
plot(customer$PaymentMethod,col="burlywood4",xlab="Payment Method")
```

### Assigning a title

* We assign the title to be "Bar-Plot for Payment Method".

```{r}
plot(customer$PaymentMethod,col="burlywood4",xlab="Payment Method",main="Bar-Plot for Payment Method")
```
### Creating histograms

* We create a histogram for the 'TotalCharges'column.


```{r}
hist(customer$TotalCharges)
```

### Histogram coloring

* We assign the color 'forestgreen'.


```{r}
hist(customer$TotalCharges,col="forestgreen")
```
### Histogram axes label

* We assign the x-axis label to the 'Total Charges'.

```{r}
hist(customer$TotalCharges,col="forestgreen",xlab = "Total Charges")
```
### Assigning a title for histogram

* We assign the title to be "Histogram for Total Charges".

```{r}
hist(customer$TotalCharges,col="forestgreen",xlab = "Total Charges",main = "Histogram for Total Charges")
```

### Creating density plots


* We create a density plot for the 'TotalCharges'column.

```{r}
ggplot(data = customer,aes(x=TotalCharges))+geom_density()
```
### Coloring density plot

* We assign the color 'maroon'

```{r}
ggplot(data = customer,aes(x=TotalCharges))+geom_density(col="maroon")
```

### Density plot axes labeling 

* We assign the x-axis label to the 'Total Charges'.

```{r}
ggplot(data = customer,aes(x=TotalCharges))+geom_density(col="maroon")+xlab("Total Charges")
```
### Assigning a title to a density plot

* We assign the title to be "Density plot for Total Charges".

```{r}
ggplot(data = customer,aes(x=TotalCharges))+geom_density(col="maroon")+xlab("Total Charges")+ggtitle("Density plot for Total Charges")

```
