---
title: "Bins Attribute in R"
author: Monalisa Roy
output: html_notebook
---

### Read the data

```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)
pharma=read.csv("Pharmacovigilance_audit_Data.csv",stringsAsFactors = T)
View(pharma)
```



### Install packages
```{r}
install.packages("ggplot2")
library(ggplot2)

```



### Create a histogram for 'Age' column using pharmacovigilance dataset.
## Set number of bins to 100
```{r}
ggplot(data = pharma,aes(x=Age))+geom_histogram(bins = 100)
```



## Assign a color 'azure' to the histogram
```{r}
ggplot(data = pharma,aes(x=Age))+geom_histogram(bins = 100,col="azure")
```


## Assign a colour 'white' to the fill attribute in geom_histogram function.
```{r}
ggplot(data = pharma,aes(x=Age))+geom_histogram(bins = 100,col="azure",fill="white")
```


### Create a histogram for 'PatientID' column using pharmacovigilance dataset.
## Assign a color 'wheat3' to the histogram
```{r}
ggplot(data = pharma,aes(x=PatientID))+geom_histogram(col="wheat3")
```


## Set number of bins to 50
```{r}
ggplot(data = pharma,aes(x=PatientID))+geom_histogram(col="wheat3",bins = 50)
```


## Assign a colour 'black' to the fill attribute in geom_histogram function.
```{r}
ggplot(data = pharma,aes(x=PatientID))+geom_histogram(col="wheat3",bins = 50,fill="black")

```


### Create a histogram using customer churn dataset.
## Assign MonthlyCharges column to the x-axis
```{r}
ggplot(data=customer,aes(x=MonthlyCharges))+geom_histogram()

```


## Set the number of bins to 80
```{r}
ggplot(data=customer,aes(x=MonthlyCharges))+geom_histogram(bins = 80)

```


## Assign a color 'violet' to the bars.
```{r}
ggplot(data=customer,aes(x=MonthlyCharges))+geom_histogram(bins = 80,col="violet")

```



## Assign a colour 'white' to the fill attribute in geom_histogram function.
```{r}
ggplot(data=customer,aes(x=MonthlyCharges))+geom_histogram(bins = 80,col="violet",fill="white")

```


## Create a histogram using customer churn dataset.
## Assign 'tenure' column to the x-axis.
```{r}
ggplot(data = customer,aes(x=tenure))+geom_histogram()

```



## Set the number of bins to 50
```{r}
ggplot(data = customer,aes(x=tenure))+geom_histogram(bins=50)

```


## Assign a color 'white' to the bars.
```{r}
ggplot(data = customer,aes(x=tenure))+geom_histogram(bins=50,col="white")

```


## Assign a colour 'black' to the fill attribute in geom_histogram function.
```{r}
ggplot(data = customer,aes(x=tenure))+geom_histogram(bins=50,col="white",fill="black")

```



