---
title: "Select function case study"
author: "Monalisa Roy"
output: html_notebook
---


### Read the data,load libraries
```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)

install.packages("deplyr")
library(deplyr)
```



#### Extract the individual columns:

## Extract the 5th column and store it in 'customer_5'
```{r}
select(customer,5)->customer_5
View(customer_5)
```



## Extract the 15th column and store it in 'customer_15'
```{r}
select(customer,15)->customer_15
View(customer_15)
```



#### Extract the column numbers 3,6,9,12,15 and 18 and store the result in 'customer_3_multiple'
```{r}
select(customer,3,6,9,12,15,18)->customer_3_multiple
View(customer_3_multiple)
```



#### Extract all the column number 10 to column number 20 and store the result in 'c_10_20'
```{r}
select(customer,10:20)->c_10_20
View(c_10_20)
```



#### Extract all the columns which start with letter'P'and store it in customer_P
```{r}
select(customer,starts_with("P"))->customer_P
View(customer_P)
```



#### Extract all the columns which end with letter 's' and store it in'customer_s'
```{r}
select(customer,ends_with("s"))->customer_s
View(customer_s)
```



