---
title: "Class function"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data,load libraries
```{r}
City_temp=read.csv("city_temperature.csv",stringsAsFactors = T)

placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)

```


### Find the class of the following attribute:

## Region
```{r}
class(City_temp$Region)

```


## Country
```{r}
class(City_temp$Country)

```

## City
```{r}
class(City_temp$City)

```

## Month
```{r}
class(City_temp$Month)

```

## Day
```{r}
class(City_temp$Day)

```

## Year
```{r}
class(City_temp$Year)

```

## AvgTemperature
```{r}
class(City_temp$AvgTemperature)

```

## OR in a single code we can find the class of different columns in the City_temp data.
```{r}
sapply(City_temp, class)

lapply(City_temp,class)
```



### After finding the class of the above attributes, convert them to the following data type:
## Vector to character.
## Gender
```{r}
as.character(placement$gender)

```



## ssc_b
```{r}
as.character(placement$ssc_b)

```

## hsc_b
```{r}
as.character(placement$hsc_b)

```


## hsc_s
```{r}
as.character(placement$hsc_s)

```


## status
```{r}
as.character(placement$status)

```


## workex
```{r}
as.character(placement$workex)

```


## specialisation
```{r}
as.character(placement$specialisation)

```


## Check the class of placement data and convert it to character data type.
```{r}
sapply(placement,class)



as.character(placement)
```







