---
title: "Col Attribute in R"
author: Monalisa Roy
output: html_notebook
---


### Read the data

```{r}
placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
View(placement)
```

### Install packages

```{r}
install.packages("ggplot2")
library(ggplot2)
```

### Create the following geom_point() where:
### 'Gender' is assigned to x-axis.'ssc_p'to y-axis, and map 'ssc_b' with col aesthetic
```{r}
ggplot(data = placement,aes(x=gender,y=ssc_p,col=ssc_b))+geom_point()
```


### 'ssc_b' is assigned to x-axis.'hsc_s'to y-axis, and map 'degree_t' with col aesthetic
```{r}
ggplot(data = placement,aes(x=ssc_b,y=hsc_s,col=degree_t))+geom_point()
```


### 'Status' is assigned to x-axis.'salary'to y-axis, and map 'specialisation' with col aesthetic
```{r}
ggplot(data = placement,aes(x=status,y=salary,col=specialisation))+geom_point()

```


### 'Degree_t' is assigned to x-axis.'etest_p'to y-axis, and map 'workex' with col aesthetic
```{r}
ggplot(data = placement,aes(x=degree_t,y=etest_p,col=workex))+geom_point()

```


### 'hsc_s' is assigned to x-axis.'hsc_b'to y-axis, and map 'gender' with col aesthetic
```{r}
ggplot(data = placement,aes(x=hsc_s,y=hsc_b,col=gender))+geom_point()

```


### 'hsc_s' is assigned to x-axis.'etest_p'to y-axis, and map 'degree_t' with col aesthetic
```{r}
ggplot(data = placement,aes(x=hsc_s,y=etest_p,col=degree_t))+geom_point()

```



