---
title: "Facet-grid-Attribute_in_R"
author: Monalisa Roy
output: html_notebook
---

### Read the data
```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)
```

### Install packages
```{r}
install.packages("ggplot2")
library(ggplot2)
```

### Build a histogram for the 'TotalCharges'column.Map 'gender'onto fill aesthetic.
### Facet the plot w.r.t 'gender'column.
```{r}
ggplot(data = customer,aes(x=TotalCharges,fill=gender))+geom_histogram()->graph1
graph1
graph1+facet_grid(~gender)
```

### Build a box-plot between 'tenure' & 'InternetSerice'.Map 'tenure' on the y-axis and 'InternetService'on the x-axis.Map 'Contract'to the fill aesthetic
### facet the plot w.r.t 'Contract' column
```{r}
ggplot(data = customer,aes(x=InternetService,y=tenure,fill=Contract))+geom_boxplot()->graph2
graph2
graph2+facet_grid(~Contract)
```


### Build a scatter plot between 'etest_p' and 'mba_p'.Map 'etest_p'on the y-axis and 'mba_p' on the x-axis.Map 'degree_t'onto col aesthetic
### facet the plot w.r.t 'degree_t'column.
```{r}
ggplot(data = placement,aes(x=mba_p,y=etest_p,col=degree_t))+geom_point()->graph3
graph3
graph3+facet_grid(~degree_t)

```









