---
title: "Fill-Attribute_in_R"
author: Monalisa Roy
output: html_notebook
---

### Read the data
```{r}
placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
View(placement)
```
### Install packages

```{r}
install.packages("ggplot2")
library(ggplot2)
```

### Build a bar-plot
### Assign ‘etest_p’ column to x-axis
```{r}
ggplot(data = placement,aes(x=etest_p))+geom_bar(col="orange")
```


### Assign ‘specialisation’column to x-axis
```{r}
ggplot(data = placement,aes(x=specialisation))+geom_bar(fill="cyan",col="orange")
```


### Assign ‘workex’ to the fill attribute
```{r}
ggplot(data = placement,aes(x=specialisation,fill=workex))+geom_bar(col="orange")

```


### Build a bar-plot for the ‘degree_t’ column
### Assign the fill color to be ‘orange’
```{r}
ggplot(data = placement,aes(x=degree_t))+geom_bar(fill="orange")

```


### Assign the boundary color to be ‘peru’
```{r}
ggplot(data = placement,aes(x=degree_t))+geom_bar(fill="orange",col="peru")

```



### Build a bar-plot for the ’hsc_s’ column assigned to x-axis and then:
### Assign ‘hsc_b’ to the fill aesthetic
```{r}
ggplot(data = placement,aes(x=hsc_s,fill=hsc_b))+geom_bar(col="purple")

```


### Assign ‘degree_t’ to the fill aesthetic
```{r}
ggplot(data = placement,aes(x=hsc_s,fill=degree_t))+geom_bar(col="cyan")

```


### Change the position of bars to ‘identity’
```{r}
ggplot(data = placement,aes(x=hsc_s,fill=degree_t))+geom_bar(position ="identity")

```


