---
title: "geom bar function case study"
author: Monalisa Roy
output: html_notebook
---
### Read the data

```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
```


### Loading the relevant plotting library

* We are going to use ggplot here. If it is not installed, then un-comment the line install(ggplot2) 

```{r}
#install(ggplot2)
library(ggplot2)
```

### Bar plot

* We build a bar-plot for the 'PhoneService'column.


```{r}
ggplot(data = customer,aes(x=PhoneService))+geom_bar()
```

### Coloring a bar plot

* We assign the fill color to be 'pink'.


```{r}
ggplot(data = customer,aes(x=PhoneService))+geom_bar(fill="pink")
```

### Coloring boundaries

* We assign the boundary color to be "peru".

```{r}
ggplot(data = customer,aes(x=PhoneService))+geom_bar(fill="pink",col="peru")
```



* Creating a bar-plot for the 'InternetService' column.


```{r}
ggplot(data = customer,aes(x=InternetService))+geom_bar()
```
### Filling aesthetic

* Assigning 'InternetService' to the fill aesthetic.


```{r}
ggplot(data = customer,aes(x=InternetService,fill=InternetService))+geom_bar()
```

* Assigning 'Contract' to the fill aesthetic.

```{r}
ggplot(data = customer,aes(x=InternetService,fill=Contract))+geom_bar()
```

### Changing position

* We change the position of bars to 'identity'

```{r}
ggplot(data = customer,aes(x=InternetService,fill=Contract))+geom_bar(position = "identity")
```


* Building a bar-plot for 'TechSupport'column


```{r}
ggplot(data = customer,aes(x=TechSupport))+geom_bar()
```

* Assigning 'Churn' to the fill aesthetic.

```{r}
ggplot(data = customer,aes(x=TechSupport,fill=Churn))+geom_bar()
```

