---
title: "geom_histogram"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data, load libraries

```{r}
placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
library(ggplot2)
```


### Creating a histogram for 'ssc_p' column

```{r}
ggplot(data = placement,aes(x=ssc_p))+geom_histogram()
```


**Assigning a color 'azure' to the histogram**

```{r}
ggplot(data = placement,aes(x=ssc_p))+geom_histogram(col="azure")

```


**Changing number of bins to 50**

```{r}
ggplot(data = placement,aes(x=ssc_p))+geom_histogram(bins=50,col="azure")

```


**Assigning a color 'cornsilk4'to the'fill' attribute in geom_histogram function**

```{r}
ggplot(data = placement,aes(x=ssc_p))+geom_histogram(bins=50,col="azure",fill="cornsilk4")

```


**Giving it a title**

```{r}
ggplot(data = placement,aes(x=ssc_p))+geom_histogram(bins=50,col="azure",fill="cornsilk4")+ggtitle("SSC Percentage")

```



### Creating a histogram for 'hsc_p'

```{r}
ggplot(data = placement,aes(x=hsc_p))+geom_histogram()

```


**Assigning a color 'wheat3' to the histogram**

```{r}
ggplot(data = placement,aes(x=hsc_p))+geom_histogram(col="wheat3")

```


**Changing number of bins to 50**

```{r}
ggplot(data = placement,aes(x=hsc_p))+geom_histogram(bins=50,col="wheat3")

```


**Assigning a color 'black'to the'fill' attribute in geom_histogram function**

```{r}
ggplot(data = placement,aes(x=hsc_p))+geom_histogram(bins=50,fill="black",col="wheat3")

```


**Giving it a title as 'HSC Percentage'**

```{r}
ggplot(data = placement,aes(x=hsc_p))+geom_histogram(bins=50,fill="black",col="wheat3")+ggtitle("HSC Percentage")

```


### Creating a histogram as per the following condition

**Assigning 'degree_p'column to the x-axis**

```{r}
ggplot(data = placement,aes(x=degree_p))+geom_histogram()

```


**Setting the number of bins to 80**

```{r}
ggplot(data = placement,aes(x=degree_p))+geom_histogram(bins=80)

```


**Assigning a color 'violet' to the bars**

```{r}
ggplot(data = placement,aes(x=degree_p))+geom_histogram(bins=80,col="violet")
```



**Assigning a color 'white'to the'fill' attribute in geom_histogram function**

```{r}
ggplot(data = placement,aes(x=degree_p))+geom_histogram(bins=80,col="violet",fill="white")

```


**Giving it a title 'Degree Percentage'**

```{r}
ggplot(data = placement,aes(x=degree_p))+geom_histogram(bins=80,col="violet",fill="white")+ggtitle("Degree Percentage")
```


### Creating a histogram with condition

**Assign 'etest_p'column to the x-axis**

```{r}
ggplot(data = placement,aes(x=etest_p))+geom_histogram()

```


**Setting the number of bins to 100**

```{r}
ggplot(data = placement,aes(x=etest_p))+geom_histogram(bins = 100)

```


**Assigning a color 'white' to the bars**

```{r}
ggplot(data = placement,aes(x=etest_p))+geom_histogram(bins = 100,col="white")
```


**Assigning a color 'black'to the'fill' attribute in geom_histogram function**

```{r}
ggplot(data = placement,aes(x=etest_p))+geom_histogram(bins = 100,col="white",fill="black")

```


**Giving it a title as 'E_test Percentage'**

```{r}
ggplot(data = placement,aes(x=etest_p))+geom_histogram(bins = 100,col="white",fill="black")+ggtitle("E-test Percentage")

```



