---
title: "geom bar attribute"
author: Monalisa Roy
output: html_notebook
---
### Read the data

```{r}
pharma=read.csv("Pharmacovigilance_audit_Data.csv",stringsAsFactors = T)
View(pharma)
```

```{r}
library(ggplot2)
```


### Building a bar_plot:
**Assign ‘LocationID’column to x-axis**


```{r}
ggplot(data = pharma,aes(x=LocationID))+geom_bar()
```


**Assigning ‘Issues’ to the fill attribute**

```{r}
ggplot(data = pharma,aes(x=LocationID,fill=Issues))+geom_bar()
```


**Setting a title to 'LocationID Plot'**


```{r}
ggplot(data = pharma,aes(x=LocationID,fill=Issues))+geom_bar()+ggtitle( "LocationID Plot")
```


### Building a bar-plot for the 'DrugID' column**

**Assigning the fill color to be 'orange'**
```{r}
ggplot(data = pharma,aes(x=DrugID,))+geom_bar(fill="orange")
```



**Assigning the boundary color to be 'peru'**
```{r}
ggplot(data = pharma,aes(x=DrugID))+geom_bar(fill="orange",col="peru")
```



**Setting title to 'DrugID Plot'**

```{r}
ggplot(data = pharma,aes(x=DrugID))+geom_bar(fill="orange",col="peru")+ggtitle("DrugID Plot")
```



### Building a bar-plot for the 'Gender'column assigned to x-axis.

**Assigning 'DrugID' to the fill aesthetic**
```{r}
ggplot(data = pharma,aes(x=Gender,fill=DrugID))+geom_bar()
```


**Assign 'Issues' to the fill aesthetic**
```{r}
ggplot(data = pharma,aes(x=Gender,fill=Issues))+geom_bar()
```



**Changing the position of the bars to 'identity'**
```{r}
ggplot(data = pharma,aes(x=Gender,fill=Issues))+geom_bar(position = "identity")
```


**Setting title to 'Gender Plot'**
```{r}
ggplot(data = pharma,aes(x=Gender,fill=Issues))+geom_bar(position = "identity")+ggtitle("Gender Plot")
```





