---
title: "geom point attribute"
author: Monalisa Roy
output: html_notebook
---
### Read the data, load libraries
```{r}
placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
library(ggplot2)
```


### Creating a scatter-plot

**Assigning  'hsc_p'column to x-axis and 'ssc_p'column to y-axis**

```{r}
ggplot(data=placement,aes(x=hsc_p,y=ssc_p))+geom_point()
```


**Mapping 'gender' to col aesthetic**

```{r}
ggplot(data=placement,aes(x=hsc_p,y=ssc_p,col=gender))+geom_point()
```



**Mapping 'workex'to col aesthetic**

```{r}
ggplot(data=placement,aes(x=hsc_p,y=ssc_p,col=workex))+geom_point()
```



**Mapping 'status to col aesthetic**
```{r}
ggplot(data=placement,aes(x=hsc_p,y=ssc_p,col=status))+geom_point()

```


**Add a title to the plot as'Comparing HSC & SSC Percentage'**

```{r}
ggplot(data=placement,aes(x=hsc_p,y=ssc_p,col=status))+geom_point()+ggtitle("Comparing HSC & SSC Percentage")

```



### Creating a scatter-plot**

**Assigning 'degree_p'column to the x-axis and 'mba_p'column to the y-axis.**


```{r}
ggplot(data=placement,aes(x=degree_p,y=mba_p))+geom_point()

```


**Using 'col' as an aesthetic and assign it the column 'status'**

```{r}
ggplot(data=placement,aes(x=degree_p,y=mba_p,col=status))+geom_point()
```


**Using 'col' as an aesthetic and assign it the column 'specialisation'**

```{r}
ggplot(data=placement,aes(x=degree_p,y=mba_p,col=specialisation))+geom_point()

```


**Adding a title to the plot as 'Understanding Degree & MBA Percentage'**
```{r}
ggplot(data=placement,aes(x=degree_p,y=mba_p,col=specialisation))+geom_point()+ggtitle("Understanding Degree & MBA Percentage")

```


### Creating a scatter-plot:


**Assigning 'etest_p'column to the x-axis and 'salary'column to the y-axis**

```{r}
ggplot(data=placement,aes(x=etest_p,y=salary))+geom_point()

```


**Use 'col' as an aesthetic and assign it the column 'workex'**

```{r}
ggplot(data=placement,aes(x=degree_p,y=mba_p,col=workex))+geom_point()
```


**Using 'col' as an aesthetic and assign it the column 'gender'**

```{r}
ggplot(data=placement,aes(x=degree_p,y=mba_p,col=gender))+geom_point()
```


**Adding a title to the plot as'E-test & Salary'**

```{r}
ggplot(data=placement,aes(x=degree_p,y=mba_p,col=gender))+geom_point()+ggtitle("E-test & Salary")
```

