---
title: "Data visualization -- Histogram"
author: Monalisa Roy
output: html_notebook
---

## Plotting histograms


```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)


library(ggplot2)
```

### Histogram for the'tenure' column


```{r}
ggplot(data = customer,aes(x=tenure))+geom_histogram()
```

### Coloring with 'mediumspringgreen'

```{r}
ggplot(data = customer,aes(x=tenure))+geom_histogram(fill="mediumspringgreen")
```

### Boundary color

```{r}
ggplot(data = customer,aes(x=tenure))+geom_histogram(fill="mediumspringgreen",col="azure")
```
### Altering the number of the bins to be 100.
```{r}
ggplot(data = customer,aes(x=tenure))+geom_histogram(fill="mediumspringgreen",col="azure",bins = 100)
```



### Histogram for the'MonthlyCharges' column.
```{r}
ggplot(data = customer,aes(x=MonthlyCharges))+geom_histogram()
```



### 'PaymentMethod' to the fill aesthetic.
```{r}
ggplot(data = customer,aes(x=MonthlyCharges,fill=PaymentMethod))+geom_histogram()
```



### Assigning 'OnlineBackup' to the fill aesthetic.
```{r}
ggplot(data = customer,aes(x=MonthlyCharges,fill=OnlineBackup))+geom_histogram()
```



### Building a histogram for the 'TotalCharges'column
```{r}
ggplot(data=customer,aes(x=TotalCharges))+geom_histogram()
```


### 'gender' to the fill aesthetic.
```{r}
ggplot(data=customer,aes(x=TotalCharges,fill=gender))+geom_histogram()
```



### Assigning 'InternetService' to the fill aesthetic.

```{r}
ggplot(data=customer,aes(x=TotalCharges,fill=InternetService))+geom_histogram()
```







