---
title: "Data visualization -- Geom_point function"
author: Monalisa Roy
output: html_notebook
---

### Read the data
```{r}

customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)

library(ggplot2)
```



### Building a scatter-plot between 'TotalCharges'and 'tenure'.Map 'TotalCharges'to the y-axis and 'tenure'to the x-axis
```{r}
ggplot(data = customer,aes(x=tenure,y=TotalCharges))+geom_point()
```




### Assign it the color 'wheat3'
```{r}
ggplot(data = customer,aes(x=tenure,y=TotalCharges))+geom_point(col="wheat3")
```




### Use 'col' as an aesthetic and map 'PaymentMethod'to col
```{r}
ggplot(data = customer,aes(x=tenure,y=TotalCharges,col=PaymentMethod))+geom_point()
```



###Use 'col' as an aesthetic and map 'gender' to col.
```{r}
ggplot(data = customer,aes(x=tenure,y=TotalCharges,col=gender))+geom_point()
```


###Map 'Dependents'to both 'col' and 'shape'aesthetics
```{r}
ggplot(data = customer,aes(x=tenure,y=TotalCharges,col=Dependents,shape=Dependents))+geom_point()

```



###.#Q1.Build a scatter-plot between 'tenure'and 'MonthlyCharges'.Map 'tenure'to the y-axis and 'MonthlyCharges'to the x-axis
```{r}
ggplot(data = customer,aes(x=MonthlyCharges, y=tenure))+geom_point()

```


###.Assign the color 'yellowgreen'.
```{r}
ggplot(data = customer,aes(x=MonthlyCharges, y=tenure))+geom_point(col="yellowgreen")

```


###.Use 'col' as an aesthetic and map 'InternetService' to col.
```{r}
ggplot(data = customer,aes(x=MonthlyCharges, y=tenure,col=InternetService))+geom_point()

```


###.Use 'col' as an aesthetic and map 'Contract' to col.
```{r}
ggplot(data = customer,aes(x=MonthlyCharges, y=tenure,col=Contract))+geom_point()

```




