---
title: "Geom box plot"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data, load libraries

```{r}
placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
library(ggplot2)
```


### Creating a box-plot between 'etest_p' & 'workex'.Map 'etest_p'to the y-axis and workex to the x-axis.

```{r}
ggplot(data = placement,aes(x=workex,y=etest_p))+geom_boxplot()

```


**Assigning it a fill color of 'wheat3'**

```{r}
ggplot(data = placement,aes(x=workex,y=etest_p))+geom_boxplot(fill="wheat3")

```


**Assigning it a boundary color of 'snow3'**

```{r}
ggplot(data = placement,aes(x=workex,y=etest_p))+geom_boxplot(fill="wheat3",col="snow3")

```


**Give a title as 'E-test & Workex'**

```{r}
ggplot(data = placement,aes(x=workex,y=etest_p))+geom_boxplot(fill="wheat3",col="snow3")+ggtitle("E-test & Workex")

```



### Build a box-plot between 'etest_p'& 'gender'. Map 'etest_p'to the y-axis and 'gender' to the x-axis.

```{r}
ggplot(data = placement,aes(x=gender,y=etest_p))+geom_boxplot()

```


**Assigning 'degree_t'to the fill aesthetic**

```{r}
ggplot(data = placement,aes(x=gender,y=etest_p,fill=degree_t))+geom_boxplot()

```


**Assign 'hsc_s'to the fill aesthetic**

```{r}
ggplot(data = placement,aes(x=gender,y=etest_p,fill=hsc_s))+geom_boxplot()

```


**Give a title as 'E-test & Gender'**

```{r}
ggplot(data = placement,aes(x=gender,y=etest_p,fill=hsc_s))+geom_boxplot()+ggtitle("E-test & Gender")

```



### Build a box-plot between 'etest_p'& 'specialisation'

```{r}
ggplot(data = placement,aes(x=specialisation,y=etest_p))+geom_boxplot()

```


#Assigning 'ssc_b'to the fill aesthetic**

```{r}
ggplot(data = placement,aes(x=specialisation,y=etest_p,fill=ssc_b))+geom_boxplot()

```



**Assigning 'hsc_b'to the fill aesthetic**

```{r}
ggplot(data = placement,aes(x=specialisation,y=etest_p,fill=hsc_b))+geom_boxplot()

```


**Giving a title as 'E-test & Specialisation'**

```{r}
ggplot(data = placement,aes(x=specialisation,y=etest_p,fill=hsc_b))+geom_boxplot()+ggtitle("E-test & Specialisation")

```