---
title: "Median function"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data,load libraries
```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)

install.packages("deplyr")
library(deplyr)

placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
View(placement)
```



## Using customer churn dataset

### Calculate the median of 'tenure'column and store it in med_tenure
```{r}
median(customer$tenure)->med_tenure
med_tenure
```



### Calculate the median of 'MonthlyCharges'column and store it in med_MonthlyCharges.
```{r}
median(customer$MonthlyCharges)->med_MonthlyCharges
med_MonthlyCharges
```



### Calculate the median of 'TotalCharges'column and store it in med_TotalCharges.
```{r}
median(customer$TotalCharges)->med_TotalCharges
na.omit(customer)->customer
med_TotalCharges
```


## Using Student Placement dataset.

### Calculate the median of percentage scored in senior secondary exams(ssc_p) and store it in med_ssc
```{r}
median(placement$ssc_p)->med_ssc
med_ssc
```



### Calculate the median of scores in higher secondary exams(hsc_p) and store it in med_hsc
```{r}
median(placement$hsc_p)->med_hsc
med_hsc
```



### Calculate the median of percentage score by students in their respective degree(degree_p)and store it in med_degree.
```{r}
median(placement$degree_p)->med_degree
med_degree

```



