---
title: "Mutate function"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data,load libraries
```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)

install.packages("deplyr")
library(deplyr)
```



### Add a column named 'Age' and assign a random value in customer churn dataset that lies within a range using sample()function based in the following conditions:

**If the customer is a senior citizen(SeniorCitizen==1),then the age assigned to the customer lies between 56 and 100.**
**If the customer is not a senior citizen (SeniorCitizen==0),then the age assigned to the customer lies between 16:55.**
```{r}
mutate(customer,ifelse(SeniorCitizen==1,sample(56:100),sample(16:55)))->Age
View(Age)
```



###Create a column named 'Customer_Category'based on the following condition.

**The customers whose monthly charges are less than 45 will be named as'Low Paying'customers.**
**The customers whose monthly charges are less than 90 will be named as'Medium Paying'customers.**
**The customers whose monthly charges are greater than 90 will be named as'High Paying'customers.**
```{r}

mutate(customer,(LowPaying=MonthlyCharges<45),(MediumPaying=MonthlyCharges<90),(HighPaying=MonthlyCharges>90))->customer_category
View(customer_category)
```



### Create a column named 'Security'based on the following condition.

**The customers who have opted for 'Online Security' will be marked as 'Secure'.**
**The customers who have not opted for 'Online Security' will be marked as 'Not Secure'.**
```{r}
mutate(customer,ifelse(OnlineSecurity=="Yes","Secure","Not Secure"))->Security
View(Security)
```



























