---
title: "Plotly in R"
author: "Monalisa Roy"
output: html_notebook
---

### Read tha data, load libraries
```{r}
install.packages("plotly")
library(plotly)

pharma=read.csv("Pharmacovigilance_audit_Data.csv",stringsAsFactors = T)
View(pharma)
```



### Build a histogram for the 'Age' column.
```{r}
plot_ly(data = pharma,x=~Age,type = "histogram")

```


**Color should be determined by 'Issues'column.**
```{r}
plot_ly(data = pharma,x=~Age,type = "histogram",color =~ Issues)

```


**Color should be determined by 'Gender'column.**
```{r}
plot_ly(data = pharma,x=~Age,type = "histogram",color =~ Gender)

```


### Create a plot between 'Age' & 'Gender' as per the following condition.

**Map 'Age' on the y-axis.**
```{r}
plot_ly(data = pharma,y=~Age,type = "scatter")

```





**Map 'Gender' on the x-axis.**
```{r}
plot_ly(data = pharma,x=~Gender,y=~Age,type="scatter",mode="markers")

```


**color should be determined by 'Issues' column.**
```{r}
plot_ly(data = pharma,x=~Gender,y=~Age,type="scatter",color =~Issues,mode="markers")

```


### Create a box-plot between 'DrugID' & 'Age'

**Map 'DrugID'on the x-axis.**
```{r}
plot_ly(data = pharma,x=~DrugID,type = "box")

```


**Map 'Age' on the y-axis**
```{r}
plot_ly(data = pharma,x=~DrugID,y=~Age,type = "box")

```


**Color should be determined by 'Gender'column.**
```{r}
plot_ly(data = pharma,x=~DrugID,y=~Age,type = "box",color =~Gender)

```





