---
title: "R Notebook"
author: Monalisa Roy
output: rmarkdown::github_document
---

### Read the data

```{r}
placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
```

### Loading the relevant plotting library

* We are going to use ggplot here. If it is not installed, then un-comment the line install(ggplot2) 

```{r}
#install(ggplot2)
library(ggplot2)
```

** Building a bar-plot

* Assigning a column to x-axis

```{r}
ggplot(data = placement,aes(x=etest_p))+geom_bar(col="orange")
```


* Assigning ‘specialisation’column to x-axis

```{r}
ggplot(data = placement,aes(x=specialisation))+geom_bar(fill="cyan",col="orange")
```



* Assigning ‘workex’ to the fill attribute

```{r}
ggplot(data = placement,aes(x=specialisation,fill=workex))+geom_bar(col="orange")
```



* Building a bar-plot for the ‘degree_t’ column

* Also we assign the fill color to be ‘orange’
* and assign the boundary color to be ‘peru’

```{r}
ggplot(data = placement,aes(x=degree_t))+geom_bar(fill="orange",col="peru")
```



* Building a bar-plot for the ’hsc_s’ column assigned to x-axis and then:

* Here we assign ‘hsc_b’ to the fill aesthetic

```{r}
ggplot(data = placement,aes(x=hsc_s,fill=hsc_b))+geom_bar(col="purple")

```

* Now we assign ‘degree_t’ to the fill aesthetic

```{r}
ggplot(data = placement,aes(x=hsc_s,fill=degree_t))+geom_bar(col="cyan")
```


* Changing  the position of bars to ‘identity’

```{r}
ggplot(data = placement,aes(x=hsc_s,fill=degree_t))+geom_bar(position ="identity")
```


