---
title: "Sample and Count function Case Study"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data,load libraries
```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)

install.packages("deplyr")
library(deplyr)

```



#### Extract 333 random records from the customer_churn dataframe and store the result in 'customer_333'
```{r}
sample_n(customer,333)->customer_333
View(customer_333)
```



#### Extract 1000 random records from the customer_churn dataframe and store the result in 'customer_1000'
```{r}
sample_n(customer,1000)->customer_1000
View(customer_1000)
```



#### Randomly extract 23% of the records from the customer_churn dataframe and store the result in'customer_23_percent'.
```{r}
sample_frac(customer,0.23)->customer_23_percent
View(customer_23_percent)
```



#### Get the count of different level from the 'PaymentMethod'columnn.
```{r}
count(customer,PaymentMethod,sort=TRUE)
```


## or
```{r}
count_(customer,"PaymentMethod",sort = TRUE)

```

#### Get the count of different levels from the 'Churn' column.
```{r}
count(customer,Churn,sort=TRUE)
```





