---
title: "Select function"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data,load libraries
```{r}
install.packages("deplyr")
library(deplyr)

placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
View(placement)

pharma=read.csv("Pharmacovigilance_audit_Data.csv",stringsAsFactors = T)
View(pharma)
```



### Extract the following columns using placement dataset.

**Extract the specialization column (12th column)and store it in s_student.**
```{r}
select(placement,12)->s_student
View(s_student)
```



**Extract the salary column (15th column)and store it in s_salary.**
```{r}
select(placement,15)->s_salary
View(s_salary)

```


**Extract the higher secondary percentage column (5th column)and store it in hsc_percent.**
```{r}
select(placement,5)->hsc_percent
View(hsc_percent)
```




### Extract the following columnsfrom the pharmacovigilance dataset.

**Extract 1st,3rd and 5th column and store it in col_135.**
```{r}
select(pharma,1,3,5)->col_135
View(col_135)
```



**Extract 2nd and 6th column and store it in col_26.**
```{r}
select(pharma,2,6)->col_26
View(col_26)
```



### EXtract column number 1 to 5 from placement dataset.
```{r}
select(placement,1:5)->col_15
View(col_15)
```



