---
title: "Standard Deviation"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data,load libraries
```{r}
install.packages("deplyr")
library(deplyr)

placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
View(placement)

customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)
```




## Using the customer churn dataset:

### Calculate the standard deviation of 'tenure'column and store it in sd_tenure.
```{r}
sd(customer$tenure)->sd_tenure
sd_tenure
```



### Calculate the standard deviation of 'MonthlyCharges'column and store it in sd_MonthlyCharges
```{r}
sd(customer$MonthlyCharges)->sd_MonthlyCharges
sd_MonthlyCharges
```



### Calculate the standard deviation of 'TotalCharges'column and store it in sd_TotalCharges.
```{r}
na.omit(customer)->customer
sd(customer$TotalCharges)->Sd_TotalCharges
Sd_TotalCharges
```



#### Using student's placement dataset:

## Calculate the standard deviation of etest and store it in sd_etest.
```{r}
sd(placement$etest_p)->sd_etest
sd_etest
```



## Calculate the standard deviation of salary and store it in sd_salary.
```{r}
na.omit(placement)->placement
sd(placement$salary)->sd_salary
sd_salary
```



## Calculate the standard deviation of percentage score by students in MBA(mba_p)and store it in sd_mba.
```{r}
sd(placement$mba_p)->sd_mba
sd_mba
```





