---
title: "Summarize function"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data,load libraries
```{r}
install.packages("deplyr")
library(deplyr)

placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
View(placement)
```



#### Using summerize()function calculate the following for etest column.
## Median
## Variance
## Standard Deviation
```{r}
summarise(placement,median=median(etest_p),var=var(etest_p),sd=sd(etest_p))

```


#### Calculate the following for MBA percentage(mba_p)of students:
## Median
## Variance
## Standard Deviation
```{r}
summarise(placement,median=median(mba_p))

summarise(placement,var=var(mba_p))

summarise(placement,sd=sd(mba_p))
```




### Calculate the median of hsc_p and group it w.r.t 'Salary'column.
```{r}
group_by(placement,salary)->new_data
summarise(new_data,hsc_median=median(hsc_p))
```


#### Calculate variance of ssc_p and group it w.r.t 'salary'column.
```{r}
group_by(placement,salary)->new_data1
summarise(new_data1,ssc_var=var(ssc_p))
```



## There are some salaries that occur only once, hence the variance is NA. 
## The following removes the NA values
```{r}
na.omit(summarise(new_data1,ssc_var=var(ssc_p)))

```


## or
```{r}
na.omit(summarise(group_by(placement,salary),ssc_var=var(ssc_p)))

```


#### Calculate standard deviation of etest_p and group it w.r.t.'Salary'
## Keeping the rows without NA in the std dev. column
```{r}
na.omit(summarise(group_by(placement,salary),etest_p_sd=sd(etest_p)))

```


## If we want to keep the NA values
```{r}
summarise(group_by(placement,salary),etest_p_sd=sd(etest_p))

```



