---
title: "Summarise function Case Study"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data,load libraries
```{r}
customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)

install.packages("deplyr")
library(deplyr)

```


#### Get the median, variance,standaerd deviation for the 'tenure'column.
```{r}
summarise(customer,median=median(tenure),var=var(tenure),sd=sd(tenure))

```





#### Get the median, variance,standaerd deviation for the 'MonthlyCharges'column.
```{r}
summarise(customer,median=median(MonthlyCharges),var=var(MonthlyCharges),sd=sd(MonthlyCharges))

```


#### Get the standard deviation of 'tenure' and group it w.r.t 'PaymentMethod'column.
```{r}
group_by(customer,PaymentMethod)->grouped
summarise(grouped,sd=sd(tenure))
```



#### Get the median of 'MonthlyCharges' and group it w.r.t 'Contract'column.
```{r}
group_by(customer,Contract)->grouped_1
summarise(grouped_1,median=median(MonthlyCharges))
```




#### Get the  variance of 'TotalCharges' and group it w.r.t'InternetService'column
```{r}

group_by(customer,InternetService)->grouped_2
summarise(grouped_2,var=var(TotalCharges))

```




