---
title: "Variance function"
author: "Monalisa Roy"
output: html_notebook
---

### Read the data,load libraries
```{r}

install.packages("deplyr")
library(deplyr)

placement=read.csv("Placement_Data_Full_Class.csv",stringsAsFactors = T)
View(placement)

customer=read.csv("customer-churn",stringsAsFactors = T)
View(customer)

```

## Using customer churn dataset:

#### Calculate the variance of 'tenure'column and store it in var_tenure
```{r}
var(customer$tenure)->var_tenure
var_tenure
```



#### Calculate the variance of 'MonthlyCharges'column and store it in var_MonthlyCharges
```{r}
var(customer$MonthlyCharges)->var_MonthlyCharges
var_MonthlyCharges
```



#### Calculate the variance of 'TotalCharges'column and store it in var_TotalCharges
```{r}
var(customer$TotalCharges)->var_TotalCharges
var_TotalCharges
```



## Using student's placement dataset:

#### Calculate the variance of percentage scored in senior secondary exams(ssc_p)and store it in var_ssc
```{r}
var(placement$ssc_p)->var_ssc
var_ssc

```



#### Calculate the variance of percentage scored in senior secondary exams(hsc_p)and store it in var_hsc.
```{r}
var(placement$hsc_p)->var_hsc
var_hsc
```



#### Calculate the variance of percentage score by students in their respective degree(degree_p)and store it in var_degree
```{r}
var(placement$degree_p)->var_degree
var_degree

```
 




